PRIMUS: Galaxy Environment on the Quiescent Fraction Evolution at $z < 1$

### 2014-08-14 qfenv_paper/qf_environment.tex
new table

\begin{table} 
  \caption{Best Fit Parameters for $f_{\rm{Q}}(\mathcal{M}_{*})$}
  \label{tab:bestfitparam}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
    $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
$0.05 < z< 0.12$ &Low           &12859                       &14443                           \\
               &High            &18952                       &13387                           \\ 
                              &               &                       &                           \\ \hline
$0.2 < z <0.4$      &Low           &1158                    &3445                           \\
               &High            &817                    &1531                           \\
               &               &                       &                           \\ \hline
$0.4 < z < 0.6$      &Low           &1315                       &3390                           \\
               &High            &848                       &1499                           \\
               &               &                       &                           \\ \hline
$0.6 < z < 0.8$      &Low           &1158                       &2303                           \\
               &High            &900                       &1275                           \\
               &               &                       &                           \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\rm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf}.  
\end{table}

>>>>

\begin{table} 
  \caption{Best Fit Parameters for $f_{\rm{Q}}(\mathcal{M}_{*})$ Fit}
  \label{tab:bestfitparam}
  \begin{center}
    \leavevmode
    \begin{tabular}{lllll} \hline \hline              
    $z_1 < z < z_2$ &Environment        &a  &b  \\ \hline 
$0.05 < z< 0.12$ &Low           &$0.3612 \pm 0.015$	&$0.482 \pm 0.006$                           \\
               &High            &18952                       &13387                           \\ 
                              &               &                       &                           \\ \hline
$0.2 < z <0.4$      &Low           &1158                    &3445                           \\
               &High            &817                    &1531                           \\
               &               &                       &                           \\ \hline
$0.4 < z < 0.6$      &Low           &1315                       &3390                           \\
               &High            &848                       &1499                           \\
               &               &                       &                           \\ \hline
$0.6 < z < 0.8$      &Low           &1158                       &2303                           \\
               &High            &900                       &1275                           \\
               &               &                       &                           \\ \hline
  \multicolumn{4}{l}{}                                             \\       
    \end{tabular} \par
    \end{center}
%    \bigskip 
    {\bf Notes}: Best fit parameters in Equation \ref{eq:qffit} for each subsample $f_{\rm{Q}}(\mathcal{M}_{*})$ in Figure \ref{fig:qf}.  
\end{table}
